Category_Tables

### 2019-08-27 Analysis/Category_Tables.Rmd
add table 2

#Summarizinig Categories

Disease_String_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Coherence.KEGG) %>% filter(!is.na(String.Coherence.KEGG)) %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(String.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(String.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(String.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes), Max_Genes = max(Number.of.genes), Mean_Genes = mean(Number.of.genes), Median_Genes = median(Number.of.genes) , Min_SNPs = min(Number.of.SNPs), Max_SNPs = max(Number.of.SNPs), Mean_SNPs = mean(Number.of.SNPs), Median_SNPs = median(Number.of.SNPs), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_String_Filt_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Filt.Coherence.KEGG) %>% filter(!is.na(String.Filt.Coherence.KEGG))   %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Filt.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(String.Filt.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(String.Filt.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(String.Filt.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes), Max_Genes = max(Number.of.genes), Mean_Genes = mean(Number.of.genes), Median_Genes = median(Number.of.genes) , Min_SNPs = min(Number.of.SNPs), Max_SNPs = max(Number.of.SNPs), Mean_SNPs = mean(Number.of.SNPs), Median_SNPs = median(Number.of.SNPs), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_Biogrid_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, Biogrid.Coherence.KEGG) %>% filter(!is.na(Biogrid.Coherence.KEGG)) %>% group_by(Category) %>% summarise(Min_Coherence = min(Biogrid.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(Biogrid.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(Biogrid.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(Biogrid.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes), Max_Genes = max(Number.of.genes), Mean_Genes = mean(Number.of.genes), Median_Genes = median(Number.of.genes) , Min_SNPs = min(Number.of.SNPs), Max_SNPs = max(Number.of.SNPs), Mean_SNPs = mean(Number.of.SNPs), Median_SNPs = median(Number.of.SNPs), Total_Networks = n()) %>% arrange(-Median_Coherence) %>% filter(Total_Networks != 0)

@@

>>>>

#Summarizing Categories

Disease_String_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Coherence.KEGG) %>% filter(!is.na(String.Coherence.KEGG)) %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(String.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(String.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(String.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_String_Filt_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, String.Filt.Coherence.KEGG) %>% filter(!is.na(String.Filt.Coherence.KEGG))   %>% group_by(Category) %>% summarise(Min_Coherence = min(String.Filt.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(String.Filt.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(String.Filt.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(String.Filt.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

Disease_Biogrid_Sum = Disease_Sum %>% dplyr::select(Disease, Category, Number.of.SNPs, Number.of.genes, Biogrid.Coherence.KEGG) %>% filter(!is.na(Biogrid.Coherence.KEGG)) %>% group_by(Category) %>% summarise(Min_Coherence = min(Biogrid.Coherence.KEGG, na.rm = TRUE), Max_Coherence = max(Biogrid.Coherence.KEGG, na.rm = TRUE), Mean_Coherence = mean(Biogrid.Coherence.KEGG, na.rm = TRUE), Median_Coherence =median(Biogrid.Coherence.KEGG, na.rm = TRUE), Min_Genes = min(Number.of.genes, na.rm = TRUE), Max_Genes = max(Number.of.genes, na.rm = TRUE), Mean_Genes = mean(Number.of.genes, na.rm = TRUE), Median_Genes = median(Number.of.genes, na.rm = TRUE) , Min_SNPs = min(Number.of.SNPs, na.rm = TRUE), Max_SNPs = max(Number.of.SNPs, na.rm = TRUE), Mean_SNPs = mean(Number.of.SNPs, na.rm = TRUE), Median_SNPs = median(Number.of.SNPs, na.rm = TRUE), Total_Networks = n()) %>% arrange(-Median_Coherence)

@@

```{r}
msig = readRDS("./data/Coherence_Results/All_Msig_String.rds")

#Correlation betweeen categories and size

msig_cor = msig %>% group_by(Category) %>% summarise(Slope_Cor = cor(Count, Slope, "complete")) %>% arrange(Slope_Cor)

colnames(msig_cor)[2] = "Size Correlation"

```{r}
options(scipen = 2)

msig_sum = msig %>% group_by(Category) %>% summarise(Min_Slope = min(Slope, na.rm = TRUE), Max_Slope = max(Slope, na.rm = TRUE), Mean_Slope = mean(Slope, na.rm = TRUE), Median_Slope = median(Slope, na.rm = TRUE), Min_Genes = min(Count), Max_Genes = max(Count), Mean_Genes = mean(Count), Median_Genes = median(Count), Total_Sets = n()) %>% arrange(Mean_Slope)

msig_sum = left_join(msig_sum, msig_cor)

#Adding in random slope

rand_string = readRDS("./data/Coherence_Results/string_random_edges.rds") %>% mutate(Category = "Random") %>% dplyr::select(Category, Count, Slope)

rand_sum = rand_string %>% group_by(Category) %>% summarise(Min_Slope = min(Slope, na.rm = TRUE), Max_Slope = max(Slope, na.rm = TRUE), Mean_Slope = mean(Slope, na.rm = TRUE), Median_Slope = median(Slope, na.rm = TRUE), Min_Genes = min(Count), Max_Genes = max(Count), Mean_Genes = mean(Count), Median_Genes = median(Count), Total_Sets = n(),) %>% arrange(Mean_Slope)

rand_sum = rand_sum %>% mutate(`Size Correlation` = cor(rand_string$Count, rand_string$Slope))

msig_sum = bind_rows(msig_sum, rand_sum)

msig_sum = msig_sum %>% rename(`Minimum Slope` = Min_Slope, `Maximum Slope` = Max_Slope, `Mean Slope` = Mean_Slope, `Median Slope` =  Median_Slope, `Minimum # Genes` = Min_Genes, `Maximum # Genes` = Max_Genes, `Mean # Genes` = Mean_Genes, `Median # Genes` = Median_Genes, `Total Networks` = Total_Sets)

msig_sum = msig_sum %>% mutate(`Minimum Slope` = format(`Minimum Slope`, digits = 3)) %>% mutate(`Maximum Slope` = format(`Maximum Slope`, digits = 3)) %>% mutate(`Mean Slope` = format(`Mean Slope`, digits = 3)) %>% mutate(`Median Slope` = format(`Median Slope`, digits = 3)) %>% mutate(`Mean # Genes` = format(`Mean # Genes`, digits = 4)) %>% mutate(`Size Correlation` = format(`Size Correlation`, digits = 2))

require(writexl)

write_xlsx(msig_sum, "../manuscript/tables/supplementary_table_S2.xlsx")
